### 2020-09-27 priority-cp.tex
Started PGV progress. Created Makefile with watch command.
Rewrote text.

\paragraph*{Priorities, types, and environments}
Types are based on CLL and range over $\ty{A}, \ty{B}, \ty{C}$. Types are annotated with priorities which range over $\cs{o} \in \mathbb{N} \sqcup \{\omega\}$. Let $\omega$ be a special element such that $\cs{o}<\omega$ for all $\cs{o}\in \mathbb{N}$. Often, we will omit $\omega$ when not necessary. \todo{check the omega thing is also part of our presentation} Types $\ty{\tyone[\cs{o}]}$ and $\ty{\tybot[\cs{o}]}$ are used to type channel endpoints which are ready to be closed. Types $\ty{\tynil[\cs{o}]}$ and $\ty{\tytop[\cs{o}]}$ are used to... Type $\ty{\tytens[\cs{o}]{A}{B}}$ (respectively, $\ty{\typarr[\cs{o}]{A}{B}}$) is used to type a channel endpoint that first {outputs} (respectively, {inputs}) a channel of type $\ty A$ and then proceeds as $\ty B$. $\ty{\typlus[\cs{o}]{A}{B}}$ is used to type a channel endpoint over which we can {select} either the \emph{left} branch and proceed as $\ty A$ or the \emph{right} branch and proceed as $\ty B$. $\ty{\tywith[\cs{o}]{A}{B}}$ is used to type a channel endpoint that can offer a both $\ty A$ and $\ty B$. A typing context $\ty\Gamma$ is a partial function associating channel names to types.
\[
\begin{array}{lcl}
  \ty{A}, \ty{B}, \ty{C}
  & \coloneqq & \ty{\tyone[\cs{o}]}
    \sep        \ty{\tybot[\cs{o}]}
    \sep        \ty{\tynil[\cs{o}]}
    \sep        \ty{\tytop[\cs{o}]}
    \sep        \ty{\tytens[\cs{o}]{A}{B}}
    \sep        \ty{\typarr[\cs{o}]{A}{B}}
    \sep        \ty{\typlus[\cs{o}]{A}{B}}
    \sep        \ty{\tywith[\cs{o}]{A}{B}}
  \\
  \ty{\Gamma}, \ty{\Delta}
  & \coloneqq & \ty{\emptyenv}
    \sep        \ty{\Gamma}, \tmty{x}{A}
\end{array}
\]

Duality on types is a total function and is defined below. It preserves priorities of types.
\[
\begin{array}{lcl}
  \ty{\co{(\tyone[\cs{o}])}} & = & \ty{\tybot[\cs{o}]} \\
  \ty{\co{(\tybot[\cs{o}])}} & = & \ty{\tyone[\cs{o}]} \\
  \ty{\co{(\tynil[\cs{o}])}} & = & \ty{\tytop[\cs{o}]} \\
  \ty{\co{(\tytop[\cs{o}])}} & = & \ty{\tynil[\cs{o}]}
\end{array}
\qquad
\begin{array}{lcl}
  \ty{\co{(\tytens[\cs{o}]{A}{B})}} & = & \ty{\typarr[\cs{o}]{\co{A}}{\co{B}}} \\
  \ty{\co{(\typarr[\cs{o}]{A}{B})}} & = & \ty{\tytens[\cs{o}]{\co{A}}{\co{B}}} \\
  \ty{\co{(\typlus[\cs{o}]{A}{B})}} & = & \ty{\tywith[\cs{o}]{\co{A}}{\co{B}}} \\
  \ty{\co{(\tywith[\cs{o}]{A}{B})}} & = & \ty{\typlus[\cs{o}]{\co{A}}{\co{B}}}
\end{array}
\]

Finally, function $\pr(\cdot)$ defined over types returns the priority of that type; function $\minpr(\cdot)$ defined over typing contexts returns the \emph{minimum} priority of all types in that context.
Both functions are defined as expected below.
\[
\begin{array}{lclclcl}
  \pr(\ty{\tyone[\cs{o}]})        & = & \cs{o}  \\
  \pr(\ty{\tybot[\cs{o}]})        & = & \cs{o}  \\
  \pr(\ty{\tynil[\cs{o}]})        & = & \cs{o}  \\
  \pr(\ty{\tytop[\cs{o}]})        & = & \cs{o}  \\
  \\
  \minpr(\ty{\emptyenv})          & = & \varnothing
\end{array}
\qquad
\begin{array}{lclclcl}
  \pr(\ty{\tytens[\cs{o}]{A}{B}}) & = & \cs{o}  \\
  \pr(\ty{\typarr[\cs{o}]{A}{B}}) & = & \cs{o}  \\
  \pr(\ty{\typlus[\cs{o}]{A}{B}}) & = & \cs{o}  \\
  \pr(\ty{\tywith[\cs{o}]{A}{B}}) & = & \cs{o}  \\
  \\
  \minpr(\ty{\Gamma},\tmty{x}{A}) & = & \minpr(\ty{\Gamma})\sqcap\minpr(\ty{A})
\end{array}
\]

@@

\begin{definition}[Action]
  A~process acts on an endpoint $\tm{x}$ if it is in one of the following forms:
  \begin{multicols}{3}
    \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item $\tm{\link{x}{y}}$ 
    \item $\tm{\link{y}{x}}$
    \item $\tm{\send{x}{y}{P}}$
    \item $\tm{\recv{x}{y}{P}}$
    \item $\tm{\close{x}{P}}$
    \item $\tm{\wait{x}{P}}$
    \item $\tm{\inl{x}{P}}$
    \item $\tm{\inr{x}{P}}$
    \item $\tm{\offer{x}{P}{Q}}$
    \item $\tm{\absurd{x}}$
    \end{itemize}
  \end{multicols}
  \noindent
  A~process is an action if it acts on on some endpoint $\tm{x}$. 
\end{definition}

@@

\begin{restatablelemma}{lempcpcanonicalforms}[Canonical Forms]
  \label{lem:pcp-canonical-forms}
  If $\seq{P}{\ty{\Gamma}}$, there exists some $\tm{Q}$ such that $\tm{P}\equiv\tm{Q}$ and $\tm{Q}$ is in canonical form.
\end{restatablelemma}
\begin{proof}
  If $\tm{P}=\tm{\halt}$, we are done. Otherwise, we move any $\nu$-binders to the top using \LabTirName{SC-ResExt}, and discard any occurrences of $\tm{\halt}$ using \LabTirName{SC-ParNil}.
\end{proof}

>>>>

\paragraph*{Priorities, types, and environments}
Types are based on classical linear logic formulas, and are annotated with priorities $\cs{o}\in\mathbb{N}$.

The types $\ty{\tytens[\cs{o}]{A}{B}}$ and $\ty{\typarr[\cs{o}]{A}{B}}$ type the endpoints of a channel over which we send or receive a channel of type $\ty{A}$, and then proceed as $\ty{B}$.
The types $\ty{\tyone[\cs{o}]}$ and $\ty{\tybot[\cs{o}]}$ type the endpoints of a channel over which we send or receive a ping, and then close the channel. These act as the units for $\ty{\tytens[\cs{o}]{A}{B}}$ and $\ty{\typarr[\cs{o}]{A}{B}}$.

The types $\ty{\typlus[\cs{o}]{A}{B}}$ and $\ty{\tywith[\cs{o}]{A}{B}}$ type the endpoints of a channel over which we can make or offer a choice between two options $\ty{A}$ or $\ty{B}$.
The types $\ty{\tynil[\cs{o}]}$ and $\ty{\tytop[\cs{o}]}$ type the endpoints of a channel over which we can make offer a choice between \emph{no options}. These act as the units for $\ty{\typlus[\cs{o}]{A}{B}}$ and $\ty{\tywith[\cs{o}]{A}{B}}$.
\[
\begin{array}{lcl}
  \ty{A}, \ty{B}, \ty{C}
  & \coloneqq & \ty{\tytens[\cs{o}]{A}{B}}
    \sep        \ty{\typarr[\cs{o}]{A}{B}}
    \sep        \ty{\tyone[\cs{o}]}
    \sep        \ty{\tybot[\cs{o}]}
    \sep        \ty{\typlus[\cs{o}]{A}{B}}
    \sep        \ty{\tywith[\cs{o}]{A}{B}}
    \sep        \ty{\tynil[\cs{o}]}
    \sep        \ty{\tytop[\cs{o}]}
\end{array}
\]
A typing context $\ty\Gamma$ is a partial function associating channel names to types.
\[
\begin{array}{lcl}
  \ty{\Gamma}, \ty{\Delta}
  & \coloneqq & \ty{\emptyenv}
    \sep        \ty{\Gamma}, \tmty{x}{A}
\end{array}
\]
Duality on types is an involutive function which preserves the priorities of types.
\[
\begin{array}{lcl}
  \ty{\co{(\tyone[\cs{o}])}} & = & \ty{\tybot[\cs{o}]} \\
  \ty{\co{(\tybot[\cs{o}])}} & = & \ty{\tyone[\cs{o}]} \\
  \ty{\co{(\tynil[\cs{o}])}} & = & \ty{\tytop[\cs{o}]} \\
  \ty{\co{(\tytop[\cs{o}])}} & = & \ty{\tynil[\cs{o}]}
\end{array}
\qquad
\begin{array}{lcl}
  \ty{\co{(\tytens[\cs{o}]{A}{B})}} & = & \ty{\typarr[\cs{o}]{\co{A}}{\co{B}}} \\
  \ty{\co{(\typarr[\cs{o}]{A}{B})}} & = & \ty{\tytens[\cs{o}]{\co{A}}{\co{B}}} \\
  \ty{\co{(\typlus[\cs{o}]{A}{B})}} & = & \ty{\tywith[\cs{o}]{\co{A}}{\co{B}}} \\
  \ty{\co{(\tywith[\cs{o}]{A}{B})}} & = & \ty{\typlus[\cs{o}]{\co{A}}{\co{B}}}
\end{array}
\]
The function $\pr(\cdot)$ returns the priority of a type. The function $\minpr(\cdot)$ returns the \emph{minimum} priority of all types a typing context.
\[
\begin{array}{lclclcl}
  \pr(\ty{\tyone[\cs{o}]})        & = & \cs{o}  \\
  \pr(\ty{\tybot[\cs{o}]})        & = & \cs{o}  \\
  \pr(\ty{\tynil[\cs{o}]})        & = & \cs{o}  \\
  \pr(\ty{\tytop[\cs{o}]})        & = & \cs{o}  \\
  \\
  \minpr(\ty{\emptyenv})          & = & \varnothing
\end{array}
\qquad
\begin{array}{lclclcl}
  \pr(\ty{\tytens[\cs{o}]{A}{B}}) & = & \cs{o}  \\
  \pr(\ty{\typarr[\cs{o}]{A}{B}}) & = & \cs{o}  \\
  \pr(\ty{\typlus[\cs{o}]{A}{B}}) & = & \cs{o}  \\
  \pr(\ty{\tywith[\cs{o}]{A}{B}}) & = & \cs{o}  \\
  \\
  \minpr(\ty{\Gamma},\tmty{x}{A}) & = & \minpr(\ty{\Gamma})\sqcap\minpr(\ty{A})
\end{array}
\]

@@

\begin{definition}[Actions]
  A~process acts on an endpoint $\tm{x}$ if it is in one of the following forms:
  \begin{multicols}{3}
    \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item $\tm{\link{x}{y}}$ 
    \item $\tm{\link{y}{x}}$
    \item $\tm{\send{x}{y}{P}}$
    \item $\tm{\recv{x}{y}{P}}$
    \item $\tm{\close{x}{P}}$
    \item $\tm{\wait{x}{P}}$
    \item $\tm{\inl{x}{P}}$
    \item $\tm{\inr{x}{P}}$
    \item $\tm{\offer{x}{P}{Q}}$
    \item $\tm{\absurd{x}}$
    \end{itemize}
  \end{multicols}
  \noindent
  A~process is an action if it acts on on some endpoint $\tm{x}$.
\end{definition}

@@

\begin{restatablelemma}{lempcpcanonicalforms}[Canonical Forms]
  \label{lem:pcp-canonical-forms}
  If $\seq{P}{\ty{\Gamma}}$, there exists some $\tm{Q}$ such that $\tm{P}\equiv\tm{Q}$ and $\tm{Q}$ is in canonical form.
\end{restatablelemma}
\begin{proof}
  If $\tm{P}=\tm{\halt}$, we are done. Otherwise, we move any $\nu$-binders to the top using \LabTirName{SC-ResExt}, and discard any superfluous occurrences of $\tm{\halt}$ using \LabTirName{SC-ParNil}.
\end{proof}
